Millions of Type Errors

### 2023-04-01 oopsla23/paper.tex
telemetry table

\usepackage{alltt}
% \usepackage{amssymb} -- already loaded by acmart
\usepackage{calc}
\usepackage{cleveref}
\usepackage{listings}
\usepackage{mathpartir}
\usepackage{pifont}
\usepackage{tikz}
\usepackage{wrapfig}
\usepackage{xcolor}
\usetikzlibrary{shapes.geometric}

@@

\title{Millions of Type Errors}
\subtitle{Non-Invasive Telemetry to Measure User Experience}

@@

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\FILL}{\textbf{FILL}}

@@

@@

https://research.swtch.com/telemetry-intro

TT:
no user ID, no machine ID,
no time-ordered traces,
public process to decide what to collect

@@

.NET SDK and .NET CLI:
crash reports, command invoked, args, hashed cwd, timings;
more listed online;
published in aggregate under CC-BY
opt-out possible~\cite{dotnet-telemetry}

>>>>

\usepackage{alltt}
% \usepackage{amssymb} -- already loaded by acmart
\usepackage{calc}
\usepackage{cleveref}
\usepackage{listings}
\usepackage{mathpartir}
\usepackage{pifont}
\usepackage{tikz}
\usepackage{wasysym}
\usepackage{wrapfig}
\usepackage{xcolor}
\usetikzlibrary{shapes.geometric}

@@

\title{Millions of Type Errors}
\subtitle{Lite Telemetry to Measure User Experience}
% lean, lite, modest, non-intrusive, private, ...

@@

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\FILL}{\textbf{FILL}}
\newcommand{\dotscale}[1]{\scalebox{0.72}{#1}}
\newcommand{\wideas}[2]{\makebox[\widthof{#2}][l]{#1}}
\newcommand{\twoline}[2]{\parbox[s]{1.4cm}{\flushleft#1\newline#2}}
\newcommand{\chkYes}{\dotscale{\CIRCLE}}
\newcommand{\chkMaybe}{\wideas{\dotscale{\Circle}}{\chkYes}}
\newcommand{\chkNo}{\wideas{}{\chkYes}}

@@

\begin{table}[t]
  \caption{Comparing telemetry systems}
  \label{t:telemetry-design}

  \begin{tabular}{l@{~}cccccc}
    &             & PII       & Session ID & Deterministic & Private Data \\\midrule
    & Transparent & \chkNo    & \chkNo     & \chkYes       & \chkNo      \\
  * & Lite        & \chkNo    & \chkYes    & \chkNo        & \chkYes     \\
    & \code{.NET} & \chkMaybe & \chkYes    & \chkYes       & \chkYes     \\
    & VS Code     & \chkYes   & \chkYes    & \chkYes       & \chkYes     \\
  \end{tabular}
\end{table}

@@

counting only, public decisions about what to count, public data,
collected weekly for a sample of clients, LastWeek field = prior day when
system gathered any data;
eg command invocations, lib stack frames, 
no user ID, no machine ID,
no time-ordered traces~\cite{transparent-telemetry}.

@@

.NET SDK and .NET CLI:
crash reports, command invoked, args, hashed cwd, timings;
more listed online;
custom builds beware inadvertant disclosure, keep your filepaths clear;
data published in aggregate under CC-BY;
opt-out possible~\cite{dotnet-telemetry}
